---
title: "Codebook"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r echo=FALSE}
mean_table<-read.csv("C:/Users/User/Desktop/Course/Data science specialization/Course 3 week 4/Codebook.csv")
```
## Readme
 
###1. The test data is manipulated first. Below are the steps
1.1 Use read.table function to read the data file.
1.2 Map the the variable in features.txt to x_Test.txt.
1.3 Select variable with names having "Mean" or "Std" for x_Test.
1.4 Merge the y_test.txt with activity.txt.
1.5 Assign 128 varabile names for 3 set of files body_acc_(x-z)_test, body_gyro_(x-z)_test, total_acc_(x-z)_test.
1.6 Use cbind function to consolidate the txt files into one file called alltest.
 
###2. Secondly, the train data is manipulated in a way similar to what we mentioned previously
2.1 Use read.table function to read the train file.
2.2 Map the the variable in features.txt to x_Train.txt
2.3 Select variable with names having "Mean" or "Std" for x_Test
2.4 Assign 128 varabile names for 3 set of files body_acc_(x-z)_train, body_gyro_(x-z)_train, total_acc_(x-z)_train.
2.5 Use cbind function to consolidate the txt files into one file called alltrain.
 
###3. Merge alltest with all alltrain data by rbind function
 
###4. Rename first 3 column name as "Activivty", "Activity Code" and "Subject"
 
###5. Calculate mean of each variable by each activity and each subject to table "mean_table"

### Below is the codebook of final result "mean_table"


```{r echo=FALSE}
library(knitr)
kable(mean_table, caption = "Code of mean_table")

```


